\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-05-09 msnbase2.Rnw
some last rephrasing

In this software note, we present version 2 of the
\texttt{MSnbase}~\cite{Gatto:2012} software, available from the
Bioconductor~\cite{Huber:2015} project. The package, like other
software such as Python-based {pyOpenMS}~\cite{Rost:2014},
spectrum\_utils~\cite{Bittremieux:2020} or
Pyteomics~\cite{Goloborodko:2013}, offers a platform that lies between
low level libraries and end-user software. \texttt{MSnbase} provides a
flexible R~\cite{R} command-line environment for metabolomics and
proteomics mass spectrometry-based applications. It lays out a sound
infrastructure to work with raw mass spectrometry, quantitative and
proteomics identification data. The package enables manipulation of
these data (for example subsetting, filtering, or accessing specific
parts thereof), a detailed step-by-step processing (for example
smoothing and centroiding of raw data, or normalisation and imputation
of quantitative data), analysis and visualisation of these data and
the development of novel computational mass spectrometry
methods~\cite{Stanstrup:2019}. Here, we focus on the new developments
pertaining to raw mass spectrometry data handling and processing.

>>>>

In this software note, we present version 2 of the
\texttt{MSnbase}~\cite{Gatto:2012} software, available from the
Bioconductor~\cite{Huber:2015} project. The package, like other
software such as Python-based {pyOpenMS}~\cite{Rost:2014},
spectrum\_utils~\cite{Bittremieux:2020} or
Pyteomics~\cite{Goloborodko:2013}, offers a platform that lies between
low level libraries and end-user software. \texttt{MSnbase} provides a
flexible R~\cite{R} command-line environment for metabolomics and
proteomics mass spectrometry-based applications. It lays out a sound
infrastructure to work with raw mass spectrometry, quantitative and
proteomics identification data. The package enables manipulation (for
example subsetting, filtering, or accessing specific parts thereof),
detailed step-by-step processing (for example smoothing and
centroiding of raw data, or normalisation and imputation of
quantitative data), analysis and visualisation of these data and the
development of novel computational mass spectrometry
methods~\cite{Stanstrup:2019}. Here, we focus on the new developments
pertaining to raw mass spectrometry data handling and processing.
